Distributions

### 2022-01-05 Ch2_distributions/Ch2_Figures.Rmd
Making a color and bw version of Figure1.

```{r Figure1, fig.width=12, fig.height=4}

@@

fam_dens_plot <- ptpl %>%
  ggplot(., aes((x = mpm))) +
  #geom_line(aes(x = mpm, group = id, color = fam_g), stat = "density", alpha = 0.8) +
  geom_line(aes(x = mpm, group = fam_g), color = "grey", 
            stat = "density", alpha = 0.8) +
  geom_line(stat = "density", color = "black", lwd = 1) +
  geom_vline(xintercept = 0, color = "grey") +
  geom_hline(yintercept = 0, color = "grey") +
  labs(y = "Density", x = "Velocity in m/min") +
    # geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[2], y = zoom_dims[3], yend = zoom_dims[3]), color = box_color) +
  # geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[2], y = zoom_dims[4], yend = zoom_dims[4]), color = box_color) +
  # geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[1], y = zoom_dims[3], yend = zoom_dims[4]), color = box_color) +
  # geom_segment(aes(x = zoom_dims[2], xend = zoom_dims[2], y = zoom_dims[3], yend = zoom_dims[4]), color = box_color) +
  theme_classic() +
  scale_color_manual(values = my.cols2) +
  theme(legend.position = "none")

@@

ggsave2(filename = "Ch2_distributions/Figures/Figure1.png")
```

>>>>

```{r Figure1col, fig.width=12, fig.height=4}

ind_dens_plot <- ptpl %>%
  ggplot(., aes((x = mpm))) +
  geom_line(aes(x = mpm, group = id, color = fam_g), stat = "density", alpha = 0.8) +
  #geom_line(aes(x = mpm, group = id), color = "grey", stat = "density", alpha = 0.8) +
  geom_line(stat = "density", color = "black", lwd = 1) +
  geom_vline(xintercept = 0, color = "grey") +
  geom_hline(yintercept = 0, color = "grey") +
  labs(y = "Density", x = "Velocity in m/min") +
  # geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[2], y = zoom_dims[3], yend = zoom_dims[3]), color = box_color) +
  # geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[2], y = zoom_dims[4], yend = zoom_dims[4]), color = box_color) +
  # geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[1], y = zoom_dims[3], yend = zoom_dims[4]), color = box_color) +
  # geom_segment(aes(x = zoom_dims[2], xend = zoom_dims[2], y = zoom_dims[3], yend = zoom_dims[4]), color = box_color) +
  theme_classic() +
  scale_color_manual(values = my.cols2) +
  theme(legend.position = "none")

fam_dens_plot <- ptpl %>%
  ggplot(., aes((x = mpm))) +
  geom_line(aes(x = mpm, group = fam_g, color = fam_g), stat = "density", alpha = 0.8) +
  #geom_line(aes(x = mpm, group = fam_g), color = "grey",stat = "density", alpha = 0.8) +
  geom_line(stat = "density", color = "black", lwd = 1) +
  geom_vline(xintercept = 0, color = "grey") +
  geom_hline(yintercept = 0, color = "grey") +
  labs(y = "Density", x = "Velocity in m/min") +
    # geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[2], y = zoom_dims[3], yend = zoom_dims[3]), color = box_color) +
  # geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[2], y = zoom_dims[4], yend = zoom_dims[4]), color = box_color) +
  # geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[1], y = zoom_dims[3], yend = zoom_dims[4]), color = box_color) +
  # geom_segment(aes(x = zoom_dims[2], xend = zoom_dims[2], y = zoom_dims[3], yend = zoom_dims[4]), color = box_color) +
  theme_classic() +
  scale_color_manual(values = my.cols2) +
  theme(legend.position = "none")

ggsave2(filename = "Ch2_distributions/Figures/Figure1_color.png")
```

```{r Figure1bw, fig.width=12, fig.height=4}

@@

fam_dens_plot <- ptpl %>%
  ggplot(., aes((x = mpm))) +
  #geom_line(aes(x = mpm, group = fam_g, color = fam_g), stat = "density", alpha = 0.8) +
  geom_line(aes(x = mpm, group = fam_g), color = "grey",stat = "density", alpha = 0.8) +
  geom_line(stat = "density", color = "black", lwd = 1) +
  geom_vline(xintercept = 0, color = "grey") +
  geom_hline(yintercept = 0, color = "grey") +
  labs(y = "Density", x = "Velocity in m/min") +
    # geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[2], y = zoom_dims[3], yend = zoom_dims[3]), color = box_color) +
  # geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[2], y = zoom_dims[4], yend = zoom_dims[4]), color = box_color) +
  # geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[1], y = zoom_dims[3], yend = zoom_dims[4]), color = box_color) +
  # geom_segment(aes(x = zoom_dims[2], xend = zoom_dims[2], y = zoom_dims[3], yend = zoom_dims[4]), color = box_color) +
  theme_classic() +
  scale_color_manual(values = my.cols2) +
  theme(legend.position = "none")

@@

ggsave2(filename = "Ch2_distributions/Figures/Figure1_bw.png")
```
